### 2015-10-28 ch05-initvals/InitialValuesPaper.tex
More outline added

%\comment{JL: 
%Focus of the article (this is what the article must reflect):

%\begin{itemize}
%\item demonstrate that a smoothed FRF, obtained as described in \cite{Lumori2014}, used as an initial estimate increases the success rate of a parametric LTI TF identification
%\item
%\comment{JL:  emphasize the importance of extending the SNR range for which the success rate is acceptable, yielding a reliable parametric estimator to be used with as little user interaction as possible.
%\end{itemize}
%}

@@

The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
Typical measurement techniques and identification strategies of transfer functions (TFs) or frequency response functions (FRFs) are discussed in \cite{Schoukens1998ImprFRFmeas,schoukens2006leakagereduction,guillaume1996,broersen1995transferfunction,pintelon2010lpm1,Antoni20071723}.
Application of these methods to real devices and systems is well-known in published literature, including \cite{Lim2010,Robinson1990,Behjat2010}.

Parametric identification of linear time-invariant (LTI) systems from input/output data has been well developed as evidenced by published literature~\cite{FDidentEd2Pintelon,Ljung1999,schoukens1999,pintGuil1998}. 
 Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
 However, in a noisy environment, the maximum likelihood estimator (MLE) engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
 Such local optima have a detrimental effect on the quality of the estimated model.

@@

In particular, two different smoothing techniques --- the time-truncated Local Polynomial Method (LPM)~\cite{Lumori2014} and the regularized finite-impulse response (RFIR)~\cite{Pillonetto201081,Chen20121525} --- are tested for different SNRs and different measurement record lengths of the input/output data of a few single-input-single-output (SISO) LTI systems.
These are compared with the existing initialization schemes, namely: (i) the generalized total least squares (GTLS), and (ii) the bootstrapped total least squares (BTLS).
%The existing initialization schemes compared with are the generalized total least squares (GTLS) and bootstrapped total least squares (BTLS).

@@

\subsection{System Setup Framework and Model}
\figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic LTI discrete-time SISO system, subjected to a known white random noise input. The following mathematical derivations pertain to discrete time systems, but they can be extended to continuous time systems as well. The full mathematical model of the system is
\begin{equation}\label{lpmtd1}
y(t)=G_0(q^{-1})u_0(t)+H_0(q^{-1})e(t)
\end{equation}
%\comment{We don't have any results with colored noise yet!}
where $G_0(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics, 
%\comment{JL: note that $H_0 = 1$ in this paper, so only white noise is considered, i.e. $e(t) = v(t)$.}, 
$e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
For white noise, $H_0 = 1$ and $e(t) = v(t)$.
Note that for simplicity, we only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this paper.
However, the generalization to continuous time is straightforward~\cite[Chapter 6]{FDidentEd2Pintelon} and has been demonstrated in Section~\ref{se:ExpMeas}.

\begin{figure}[tbh] %top bottom here
\centering
\input{\thisDir/fig/oesetup.tikz}
\caption{SISO LTI discrete-time system in an output error setup.}
\label{fig:oesetup}
\end{figure}

Numerous parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \cite{Ljung1999,Soderstrom1989}.

@@

From~\cite[Section 6.3.2.]{FDidentEd2Pintelon}, in the frequency domain, and for the DFTs (Discrete Fourier Transforms) of the windowed signals, equation \eqref{ABpolys} is of the form
\begin{align}
A(e^{-j\omega_k})Y_0(k) = B(e^{-j\omega_k})U_0(k) + I(e^{-j\omega_k})
\label{DFTspectra}
\end{align}
with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the initial and end conditions. 
In this paper, it is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.

@@

The maximum likelihood estimate of the parameter vector $\theta$  containing the coefficients of the $A$, $B$ and $I$  polynomials is obtained by solving the optimization problem
\begin{equation}
  \hat{\theta} = \arg\min_\theta V(\theta) \text{.}
\end{equation}
Since the noise $v(t)$ is assumed to be Gaussian, $V(\theta)$ accords to the weighted least squares cost function~\cite[Section 9.11]{FDidentEd2Pintelon}:
\begin{equation}\label{eq:MLEcf}
V(\theta) = \sum_{k=1}^{N/2-1}\frac{|\varepsilon(k,\theta)|^2}{\sigma_\varepsilon^2(k,\theta)}
\end{equation}
for $N$ measurements and when $\varepsilon$ denotes the error in equation (\ref{DFTspectra}),  \emph{viz}.:
\begin{align}
\varepsilon(k,\theta) = A(k,\theta)Y(k) - B(k,\theta)U(k) - I(k,\theta)\text{.}
\end{align}
The variance of the error is of the form:
\begin{equation}\label{eq:sigmaEps}
\begin{split}
\sigma_\varepsilon^2(k,\theta) 
  &=  |A(k,\theta)|^2\sigma_Y^2(k) 
   +  |B(k,\theta)|^2\sigma_U^2(k) \\
  &- 2\;\mathrm{real} \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
\end{split}
\end{equation}
where $\sigma_Y^2$ is independent of $k$ for white noise, %assumed to be a known error variance \comment{JL: why should the error variance be known? where do you use that? how do you compute it?} of the measured output spectrum $Y$ \comment{JL: relate the output error variance with the variance of $v(t)$. Isn't it the same thing?},
%\comment{this is true for white noise, and for the scaling of the DFT by $\sqrt{N}$. I think it is more clear to use the frequency domain variance instead: $\sigma_Y^2$}
and the input error variance is assumed to be zero, i.e. $\sigma^2_U=0$, and similarly, the covariance $\sigma_{YU} = 0$.
Here, $\overline{B}$ denotes the complex conjugate of $B$.
%\comment{use $\sigma^2_U$ instead}

Consequently, $V(\theta)$ is a non-quadratic function of $\theta$ which, in general, results in a non-convex optimization problem. 
The Levenberg-Marquardt~\cite{Marquardt1963} algorithm (see Algorithm~\ref{LMalgo}) is used to solve this optimization problem deterministically.
Such an approach requires good initial estimates of $\theta$ to avoid inherent local optima, which is the focus of this paper.

\begin{algorithm}
\caption{Levenberg-Marquardt~\cite{Marquardt1963}, \cite[Sec. 9.L.4]{FDidentEd2Pintelon}}\label{LMalgo}
\begin{algorithmic}[1]
  \Statex Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon^{\TT} \epsilon$. 
  \Statex The iterations start at $\atIter[0]{\theta} = \theta^{\mathrm{init}}$ and $\lambda = \max(\sigma)/100$.
%\Function{LevenbergMarquardt}{$V(\theta), \atIter[0]{\theta}$}
   \For{$i$ \textbf{in} $1 \to \infty$}
      \State $U \, \Sigma \, W^{\TT} \gets \mathtt{svd}\left( \frac{\partial \epsilon}{\partial \theta}\right)$ with $\mathrm{diag}(\Sigma) = [\sigma_1, \ldots, \sigma_n]$
      % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
      \State $\sigma_k \gets \sigma_k / (\sigma_k^2 + \lambda^2) \quad \forall k \in \{1, \ldots, n\}$
      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon$
      \State $\atIter[i]{\theta} \gets (\atIter[i-1]{\theta} + \delta\theta) / \snorm{\atIter[i-1]{\theta} + \delta\theta} $
      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$}
          \State $\lambda \gets 10 \lambda$ and then retry at $i \gets i - 1$
      \Else
          \State $\lambda \gets 0.4 \lambda$
      \EndIf
      \State \textbf{if} $\snorm{\delta\theta}/\snorm{\atIter[i]{\theta}} < n_{\theta}  \cdot 10^{-6} $ \textbf{then} \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
   \EndFor
%\EndFunction
\end{algorithmic}
\end{algorithm}

\begin{remark}
Alternatively, stochastic optimization algorithms~\cite{Spall2012,Press2007} are less likely to get stuck in local optima since many randomized initial estimates are tried.
This obviously comes with a huge computational cost compared to `classical' deterministic schemes where only a single or a few initial estimates are used to start the expensive iterative optimization procedure.
Stochastic optimization is not discussed in the remainder of this paper.
\end{remark}

@@

\begin{figure}
  \centering
  \includegraphics
  [width=0.95\onecolumnwidth]{\thisDir/fig/flowgraph}
  \caption{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using BTLS and GTLS starting values, and the novel methods outlined in this paper (3, 4).
  The flow of non-parametric data is depicted by full arrows, with the FRF data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
\end{figure}

@@

%\JL{The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \cite{pintGuil1998}. These are modifications of \eqref{eq:MLEcf}, which still take into account the noise information, while keeping the quadratic nature w.r.t.\ $\theta$. These estimators preserve consistency (which is an asymptotic behaviour, i.e.\ for $N\to\infty$). Their finite sample behaviour is prone to be improved by the FRF smoothing tools, described below.}

The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \cite{pintGuil1998}. These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t. $\theta$. 
These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
Their finite sample behavior is suitable for improvement by the FRF smoothing tools, described below.

@@

A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows \cite{Lumori2014}. Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}. The smooth characteristics of both the exact FRF $G_0$ and the transient term
%the leakage 
$T$ 
%from transients 
allow for an optimal application of the LPM, leading to a smooth FRF estimate with the transient suppressed.
%the elimination of both the leakage and interpolation errors.

  With reference to a detailed discussion in~\cite{Lumori2014}, the LPM utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. In this paper, $n=3$.

@@

\emph{Impulse response truncation}. 
%\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\cite{Lumori2014}.
%\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.

The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.
\begin{equation}
  g_{\mathrm{trunc}}(t) = 
  \begin{cases}
    g_{\text{poly}}(t) & t \leq \tau_{\mathrm{trunc}} \\
    0                    & t \geq \tau_{\mathrm{trunc}}
  \end{cases}
  \text{.}
\end{equation}
To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of the impulse response $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
Then, $\tau_{\mathrm{trunc}}$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
\begin{equation}
  \tau_{\mathrm{trunc}} = \min \left\{  t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g \right\}
  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
  \text{,}
\end{equation}
where $\gamma=1$ was used in this paper for simplicity.
By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
This can lead to a significant improvement over the classical LPM~\cite{Lumori2014}.

@@

An implementation of the RFIR estimator is available as the \texttt{arx} function in the System Identification Toolbox since \MATLAB 2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \texttt{arxoptions}. 
The hyperparameters can be determined via \texttt{arxregul}.
More information about the RFIR estimator can be found in
~\cite{Pillonetto201081,Chen20121525}. 
The DFT of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
\end{enumerate}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\onecolumnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/exampleSystems.tikz}
 % \caption{Results of an example of Monte Carlo simulation.}
 \caption{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $G_0$~\legref{leg:example-exact} under test.
 Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
\label{fig:exampleFRF}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\onecolumnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
 \caption{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
 The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
 $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart as a reference. }
  \label{fig:single-sim}
\end{figure}

@@

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
The confidence intervals are calculated via the Clopper-Pearson method~\cite{Clopper1934} (as implemented in \MATLAB's \texttt{binofit}).
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\cite{Ross2003}.
Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.

@@

\subsection{Experimental Setup}
The \BK{} 1613 Octave Filter Set consists of sixth-order Chebyshev band-pass filters~\cite{datasheet_bk1613}, from which we only examined the filter with a center frequency of $4\unit{kHz}$.

>>>>

\TODO{import references into main bibliography}
%\comment{JL: 
%Focus of the article (this is what the article must reflect):

%\begin{itemize}
%\item demonstrate that a smoothed FRF, obtained as described in \citep{Lumori2014}, used as an initial estimate increases the success rate of a parametric LTI TF identification
%\item
%\comment{JL:  emphasize the importance of extending the SNR range for which the success rate is acceptable, yielding a reliable parametric estimator to be used with as little user interaction as possible.
%\end{itemize}
%}

@@

The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
Typical measurement techniques and identification strategies of transfer functions (TFs) or frequency response functions (FRFs) are discussed in \citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,Guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni20071723}.
Application of these methods to real devices and systems is well-known in published literature, including \citep{Lim2010,Robinson1990,Behjat2010}.

Parametric identification of linear time-invariant (LTI) systems from input/output data has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,schoukens1999,pintGuil1998}. 
 Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
 However, in a noisy environment, the maximum likelihood estimator (MLE) engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
 Such local optima have a detrimental effect on the quality of the estimated model.

@@

In particular, two different smoothing techniques --- the time-truncated Local Polynomial Method (LPM)~\citep{Lumori2014} and the regularized finite-impulse response (RFIR)~\citep{Pillonetto201081,Chen20121525} --- are tested for different SNRs and different measurement record lengths of the input/output data of a few single-input-single-output (SISO) LTI systems.
These are compared with the existing initialization schemes, namely: (i) the generalized total least squares (GTLS), and (ii) the bootstrapped total least squares (BTLS).
%The existing initialization schemes compared with are the generalized total least squares (GTLS) and bootstrapped total least squares (BTLS).

@@

\subsection{System Setup Framework and Model}
\figref{fig:oesetup} depicts a schematic of the output error framework for  a generalized (single- or multiple-order) resonating, dynamic LTI discrete-time SISO system, subjected to a known white random noise input. The following mathematical derivations pertain to discrete time systems, but they can be extended to continuous time systems as well. The full mathematical model of the system is
\begin{equation}\label{lpmtd1}
y(t)=G_0(q^{-1})u_0(t)+H_0(q^{-1})e(t)
\end{equation}
%\comment{We don't have any results with colored noise yet!}
where $G_0(q^{-1})$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q^{-1})e(t)$ is the noise source at the output, $H_0(q^{-1})$ is the noise dynamics, 
%\comment{JL: note that $H_0 = 1$ in this paper, so only white noise is considered, i.e. $e(t) = v(t)$.}, 
$e(t)$ is white Gaussian noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-mT_{\mathrm{s}})$  with $m$ a positive integer and $T_{\mathrm{s}}$ the sampling time).
For white noise, $H_0 = 1$ and $e(t) = v(t)$.
Note that for simplicity, we only treat the discrete-time case (i.e. $t = n \cdot T_{\mathrm{s}}$ for integer values of $n$) theoretically in this paper.
However, the generalization to continuous time is straightforward~\citep[Chapter 6]{Pintelon2012} and has been demonstrated in Section~\ref{se:ExpMeas}.

\begin{figure}[tbh] %top bottom here
\centering
\input{\thisDir/fig/oesetup.tikz}
\caption[Output-error set-up.]{SISO LTI discrete-time system in an output error setup.}
\label{fig:oesetup}
\end{figure}

Numerous parametric identification techniques are devoted to the development of parametric plants $G(q^{-1},\theta)$ and parametric noise models  $H(q^{-1},\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}.

@@

From~\citep[Section 6.3.2.]{Pintelon2012}, in the frequency domain, and for the DFTs (Discrete Fourier Transforms) of the windowed signals, equation \eqref{ABpolys} is of the form
\begin{align}
A(e^{-j\omega_k})Y_0(k) = B(e^{-j\omega_k})U_0(k) + I(e^{-j\omega_k})
\label{DFTspectra}
\end{align}
with $q^{-1}$ sampled in  $q_k^{-1} = e^{-j\omega_k}$, where $\omega_k = \frac{2\pi k}{N}$ are the DFT frequencies, and $I$ is a polynomial of order $\max(N_a,N_b) - 1$, which depends on the initial and end conditions. 
In this paper, it is assumed that the orders of the polynomials $A$, $B$ and $I$ are known.

@@

The maximum likelihood estimate of the parameter vector $\theta$  containing the coefficients of the $A$, $B$ and $I$  polynomials is obtained by solving the optimization problem
\begin{equation}
  \hat{\theta} = \arg\min_\theta V(\theta) \text{.}
\end{equation}
Since the noise $v(t)$ is assumed to be Gaussian, $V(\theta)$ accords to the weighted least squares cost function~\citep[Section 9.11]{Pintelon2012}:
\begin{equation}\label{eq:MLEcf}
V(\theta) = \sum_{k=1}^{N/2-1}\frac{|\varepsilon(k,\theta)|^2}{\sigma_\varepsilon^2(k,\theta)}
\end{equation}
for $N$ measurements and when $\varepsilon$ denotes the error in equation (\ref{DFTspectra}),  \emph{viz}.:
\begin{align}
\varepsilon(k,\theta) = A(k,\theta)Y(k) - B(k,\theta)U(k) - I(k,\theta)\text{.}
\end{align}
The variance of the error is of the form:
\begin{equation}\label{eq:sigmaEps}
\begin{split}
\sigma_\varepsilon^2(k,\theta) 
  &=  |A(k,\theta)|^2\sigma_Y^2(k) 
   +  |B(k,\theta)|^2\sigma_U^2(k) \\
  &- 2\;\mathrm{real} \left( A(k,\theta) \overline{B(k,\theta)} \sigma_{YU}(k) \right)
\end{split}
\end{equation}
where $\sigma_Y^2$ is independent of $k$ for white noise, %assumed to be a known error variance \comment{JL: why should the error variance be known? where do you use that? how do you compute it?} of the measured output spectrum $Y$ \comment{JL: relate the output error variance with the variance of $v(t)$. Isn't it the same thing?},
%\comment{this is true for white noise, and for the scaling of the DFT by $\sqrt{N}$. I think it is more clear to use the frequency domain variance instead: $\sigma_Y^2$}
and the input error variance is assumed to be zero, i.e. $\sigma^2_U=0$, and similarly, the covariance $\sigma_{YU} = 0$.
Here, $\overline{B}$ denotes the complex conjugate of $B$.
%\comment{use $\sigma^2_U$ instead}

Consequently, $V(\theta)$ is a non-quadratic function of $\theta$ which, in general, results in a non-convex optimization problem. 
The Levenberg-Marquardt~\citep{Marquardt1963} algorithm (see Algorithm~\ref{LMalgo}) is used to solve this optimization problem deterministically.
Such an approach requires good initial estimates of $\theta$ to avoid inherent local optima, which is the focus of this paper.

\begin{algorithm}
\caption{Levenberg-Marquardt~\citep{Marquardt1963}, \citep[Sec. 9.L.4]{Pintelon2012}}\label{LMalgo}
\begin{algorithmic}[1]
  \Statex Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon^{\TT} \epsilon$. 
  \Statex The iterations start at $\atIter[0]{\theta} = \theta^{\mathrm{init}}$ and $\lambda = \max(\sigma)/100$.
%\Function{LevenbergMarquardt}{$V(\theta), \atIter[0]{\theta}$}
   \For{$i$ \textbf{in} $1 \to \infty$}
      \State $U \, \Sigma \, W^{\TT} \gets \mathtt{svd}\left( \frac{\partial \epsilon}{\partial \theta}\right)$ with $\mathrm{diag}(\Sigma) = [\sigma_1, \ldots, \sigma_n]$
      % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
      \State $\sigma_k \gets \sigma_k / (\sigma_k^2 + \lambda^2) \quad \forall k \in \{1, \ldots, n\}$
      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon$
      \State $\atIter[i]{\theta} \gets (\atIter[i-1]{\theta} + \delta\theta) / \snorm{\atIter[i-1]{\theta} + \delta\theta} $
      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$}
          \State $\lambda \gets 10 \lambda$ and then retry at $i \gets i - 1$
      \Else
          \State $\lambda \gets 0.4 \lambda$
      \EndIf
      \State \textbf{if} $\snorm{\delta\theta}/\snorm{\atIter[i]{\theta}} < n_{\theta}  \cdot 10^{-6} $ \textbf{then} \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
   \EndFor
%\EndFunction
\end{algorithmic}
\end{algorithm}

\begin{remark}
Alternatively, stochastic optimization algorithms~\citep{Spall2012,Press2007} are less likely to get stuck in local optima since many randomized initial estimates are tried.
This obviously comes with a huge computational cost compared to `classical' deterministic schemes where only a single or a few initial estimates are used to start the expensive iterative optimization procedure.
Stochastic optimization is not discussed in the remainder of this paper.
\end{remark}

@@

\begin{figure}
  \centering
  \includegraphics
  [width=0.95\onecolumnwidth]{\thisDir/fig/flowgraph}
  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using BTLS and GTLS starting values, and the novel methods outlined in this paper (3, 4).
  The flow of non-parametric data is depicted by full arrows, with the FRF data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
\end{figure}

@@

%\JL{The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}. These are modifications of \eqref{eq:MLEcf}, which still take into account the noise information, while keeping the quadratic nature w.r.t.\ $\theta$. These estimators preserve consistency (which is an asymptotic behaviour, i.e.\ for $N\to\infty$). Their finite sample behaviour is prone to be improved by the FRF smoothing tools, described below.}

The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}. These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t. $\theta$. 
These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
Their finite sample behavior is suitable for improvement by the FRF smoothing tools, described below.

@@

A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows \citep{Lumori2014}. Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}. The smooth characteristics of both the exact FRF $G_0$ and the transient term
%the leakage 
$T$ 
%from transients 
allow for an optimal application of the LPM, leading to a smooth FRF estimate with the transient suppressed.
%the elimination of both the leakage and interpolation errors.

  With reference to a detailed discussion in~\citep{Lumori2014}, the LPM utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. In this paper, $n=3$.

@@

\emph{Impulse response truncation}. 
%\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014}.
%\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.

The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.
\begin{equation}
  g_{\mathrm{trunc}}(t) = 
  \begin{cases}
    g_{\text{poly}}(t) & t \leq \tau_{\mathrm{trunc}} \\
    0                    & t \geq \tau_{\mathrm{trunc}}
  \end{cases}
  \text{.}
\end{equation}
To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of the impulse response $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
Then, $\tau_{\mathrm{trunc}}$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
\begin{equation}
  \tau_{\mathrm{trunc}} = \min \left\{  t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g \right\}
  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
  \text{,}
\end{equation}
where $\gamma=1$ was used in this paper for simplicity.
By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
This can lead to a significant improvement over the classical LPM~\citep{Lumori2014}.

@@

An implementation of the RFIR estimator is available as the \texttt{arx} function in the System Identification Toolbox since \MATLAB 2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \texttt{arxoptions}. 
The hyperparameters can be determined via \texttt{arxregul}.
More information about the RFIR estimator can be found in
~\citep{Pillonetto201081,Chen20121525}. 
The DFT of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
\end{enumerate}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\onecolumnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/exampleSystems.tikz}
 % \caption{Results of an example of Monte Carlo simulation.}
 \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of some successful~\legref{leg:example-good-estimate} and failed~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $G_0$~\legref{leg:example-exact} under test.
 Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
\label{fig:exampleFRF}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\onecolumnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
 \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
 The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
 $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart as a reference. }
  \label{fig:single-sim}
\end{figure}

@@

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \texttt{binofit}).
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.

@@

\subsection{Experimental Setup}
The \BK{} 1613 Octave Filter Set consists of sixth-order Chebyshev band-pass filters~\citep{datasheet_bk1613}, from which we only examined the filter with a center frequency of $4\unit{kHz}$.
